
\section{Tracking Donations, Donors, and Prospects}
\label{sec:donor}

Audience1st is particularly useful not only for tracking your donations
and donors, but also for keeping track of your ``prospecting
activities''---your contacts with individual donors and prospective
donors.  This section describes how to use these features.

\subsection{Donations, Account Codes, and Funds}
\label{sec:donations}

Recording a donation requires three pieces of information in addition to
the amount: 
the method of payment (cash, in-kind goods or services, Web donation
with a credit card, etc.), the fund that receives the donation, and
(optionally) the account code.

\begin{itemize}
\item[Payment method] Audience1st predefines a set of payment methods,
  including In-Kind Goods or Services for donations.
\item[Fund] You can choose to specify a fund, e.g. if you'd like to
  separately track donations for different campaigns.  Audience1st
  predefines only the General Fund.  To add new funds, click the
  Donations navigation tab and click the Add/Edit Donation Funds link. 
\item[Account Code] The account code is optional but may help you 
  reconcile or import Audience1st reports into external bookkeeping
  software such as QuickBooks.  You don't have to setup Account Codes in
  advance as you do with Donation Funds and other entities; you just
  enter the account code at the time the donation is recorded.  (See
  below for donations that are automatically recorded as a result of
  online purchase.)
\end{itemize}

\subsection{Recording Donations}
\label{sec:recording_donations}

To manually record a donation, navigate to the donor's account page (see
section~\ref{sec:boa-admin}) and in the yellow Admin Navbar, click
\emph{Record Donation}.  You'll be prompted to enter the donation
amount, payment method, destination fund, and optional account code.
There's a shortcut next to the Donation Fund menu to let you quickly set
up a new target Fund if necessary. 


\subsubsection{Online Cash Donations}
\label{sec:online_donations}


\subsubsection{Other Donations}
\label{sec:other_donations}


\subsection{Donation Reports}
\label{sec:donation_search}

\subsection{Prospect Tracking}
\label{sec:prospect_tracking}

Audience1st makes it easy to keep notes on each contact with a
prospective donor and even receive email reminders when a followup
contact is due.

\subsubsection{Recording A Visit}
\label{sec:prospect_visit}

\subsubsection{Showing Visits Made To A Prospect}

\subsubsection{Showing Visits Made By A Staff Member}

\subsubsection{Automatic Visit Follow-Up Email}

