\section{Troubleshooting and Maintenance}

\subsection{Backups}
\label{sec:backups}

A1 Patron Systems backs up all Audience1st databases nightly at
approximately 3~AM Pacific time.  At any given time, the following
backups are available:

\begin{itemize}
\item Nightly backups for each of the last 30 calendar days
\item Monthly backups taken on the first of the month, every month from
  the past 5 years (or from the beginning of service, whichever is later)
\end{itemize}

So, for example, on April  4, the following backups will be
available: nightly snapshots for any day from March 2 to April 3;
and snapshots for April 1, March 1, February 1, January 1, and the
first of each previous  month up to five years ago (or the beginning of
service, whichever is later).

Backups are kept encrypted on Amazon's S3 (Simple Storage Service) which
replicates data extensively for reliability.
If you use A1 Patron Systems' optional Web Hosting Service, your Web
content databases are backed up according to the same schedule.

These backups are intended for disaster recovery, not as an ``undo''
for user errors.  A technical support fee applies to restoring from
backup.  Furthermore, if restoring from an older backup and the data
schema has changed, the data will be provided only as CSV files rather
than loaded into the database.  Also, if you request old data to be
loaded into the database, new data and changes made since the time of
the loaded backup will be lost.


\subsection{Recovering From Common Mistakes}
\label{sec:recovering}

TBD

\subsection{Technical Troubleshooting}

TBD
